MS Technical Paper: \\ Placement Algorithms for Heterogeneous FPGAs

### 2025-04-28 latex/paper/paper.tex
dedicated netlist explanation

        \item \textbf{Synthesis:} 
            The synthesis tool parses the HDL source, performs logical optimizations, and maps the design onto primitive cells that suit the target FPGA technology. 
            The output is typically a \emph{structural} netlist (e.g., EDIF or structural Verilog) which details how the design’s logic is broken down into LUTs, FFs, and other vendor-specific cells.

@@

\section{RapidWright API}
    \label{sec:rapidwright_api}

@@

\section{Simulated Annealing}
    \label{sec:simulated_annealing}
    With a basic understanding of FPGA architecture, design placement, and RapidWright, we have all the necessary pieces to implement our SA placer. 
    Here we outline in detail each substage of our implementation: PrePacking, Packing, and Placement. 
    Shown in Figure \ref{fig:edif_design_device} shows an overview of the placement workflow.

@@

        The raw post-synthesis netlist only tells us the instantiated cells and the nets between them. 
        It does not report the presence of any cell structures (CARRY4 chains, etc.). 
        Thus, we must traverse the netlist to detect these cell structures and store that structure information in a class we will call \texttt{PrepackedDesign}.

>>>>

        \item \textbf{Synthesis:} 
            The synthesis tool parses the HDL source, performs logical optimizations, and maps the design onto primitive cells that suit the target FPGA technology. 
            The output is typically a structural \texttt{netlist} (e.g., EDIF or structural Verilog) which details how the design’s logic is broken down into LUTs, FFs, and other vendor-specific cells.

@@

\newpage
\section{RapidWright API}
    \label{sec:rapidwright_api}

@@

\newpage
\section{What is a Netlist?}
    \label{sec:netlist}
    In its simplest form, a netlist consists of a list of every component in an electronic design and a list of nets they connect to. 
    Here, a net, or network, denotes any group of two or more interconnected elements - whether they be transistors, logic gates, or higher-level macrocells. 
    More precisely, nets attach to component pins, and those pins reside on cells, each of which exposing multiple ports. 
    In this way, a netlist makes explicit both the individual building blocks of a circuit and the precise wiring that links them.

    In Vivado, a Netlist can be synthesized as a Hierarchical or a Flattened netlist. 
    Figure ~\ref{fig:hierarchical_design} shows the Verilog code for a simple HDL design using module instance hierarchy. 
    Figure ~\ref{fig:hier_netlist} shows the design synthesized into a hierarchical netlist, while Figure ~\ref{fig:flat_netlist} shows the same design synthesized into a flat netlist. 
    In a synthesized Netlist, the leaf cells (lowest-level cells) are necessarily primitive cells from the vendor primitives library such as LUT6, FDRE, CARRY4, DSP48E1, etc..

    \end{multicols}
    {
        \raggedright
        \includegraphics[valign=t, scale=0.3]{figures/netlist_synth/top_level.png}
        \includegraphics[valign=t, scale=0.3]{figures/netlist_synth/module_0.png}
        \includegraphics[valign=t, scale=0.3]{figures/netlist_synth/module_1.png}
        \includegraphics[valign=t, scale=0.3]{figures/netlist_synth/module_2.png}
        \includegraphics[valign=t, scale=0.3]{figures/netlist_synth/module_3.png}
        \captionof{figure}{A simple HDL design with module hierarchy.}
        \label{fig:hierarchical_design}
    }
    {
        \centering
        \includegraphics[valign=c, width=11.5cm]{figures/netlist_synth/hier_netlist.png}
        \includegraphics[valign=c, width=6cm]{figures/netlist_synth/hier_graph.png}
        \captionof{figure}{
            \textbf{Left:} A hierarchical netlist consisting of LUTs and FFs.
            \textbf{Right:} The cell hierarchy graph.
        }
        \label{fig:hier_netlist}
    }
    \vspace{0.5cm}
    {
        \centering
        \includegraphics[valign=c, width=10cm]{figures/netlist_synth/flat_netlist.png}
        \includegraphics[valign=c, width=4cm]{figures/netlist_synth/flat_graph.png}
        \captionof{figure}{
            \textbf{Left:} A flattened netlist consisting of LUTs and FFs.
            \textbf{Right:} The flattened cell hierarchy graph.
        }
        \label{fig:flat_netlist}
    }
    \begin{multicols}{2}

    RapidWright offers an easy way to access, read, or manipulate this netlist for a given HDL design. 
    Shown in Figure~\ref{fig:netlist_syn}

    Verilog \texttt{module}s are represented simply as

    .

\newpage
\section{Simulated Annealing}
    \label{sec:simulated_annealing}
    With a basic understanding of FPGA architecture, design placement, and RapidWright, we have all the necessary pieces to implement our SA placer. 
    Here we outline in detail each substage of our implementation: PrePacking, Packing, and Placement. 
    Shown in Figure \ref{fig:edif_design_device} shows an overview of the placement workflow.

@@

        The raw post-synthesis netlist only tells us the list of nets and the cell ports that they connect to. 
        It does not report the presence of any macro cell structures (CARRY4 chains, etc.). 
        Thus, we must traverse the netlist to detect these cell structures and store that structure information in a class we will call \texttt{PrepackedDesign}.
